CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-08-08 paper.Rmd
Ignore _targets

```{r}
# Available on CRAN
# library(matsbyname)
# library(matsindf)
# library(RCLabels)

@@

# Use the PFUSetup package to establish paths for the example
home_path <- "ExampleFolder"
iea_folder_path <- file.path(home_path, "IEA extended energy balance data")
iea_data_path <- file.path("IEA extended energy balance data",
                           "GH-ZA-TJ-Extended-Energy-Balances-sample-2022.csv")
setup <- PFUSetup::get_abs_paths(home_path = file.path("ExampleFolder"), 
                                 dropbox_path = "",
                                 project_path = "",
                                 iea_folder_path = iea_folder_path,
                                 iea_data_path = iea_data_path,
                                 version = "v_example")
```

>>>>

```{r}
# Available on CRAN
library(targets)

@@

# Use the PFUSetup package to establish paths for the example
home_path <- "ExampleFolder"
iea_folder_path <- file.path(home_path, "IEA extended energy balance data")
iea_data_path <- file.path("IEA extended energy balance data",
                           "GH-ZA-TJ-Extended-Energy-Balances-sample-2022.csv")
setup <- PFUSetup::get_abs_paths(home_path = file.path("ExampleFolder"), 
                                 dropbox_path = "",
                                 project_path = "",
                                 iea_folder_path = iea_folder_path,
                                 iea_data_path = iea_data_path,
                                 version = "v_example")

# Run the PFUDatabase pipeline
targets::tar_make(script = file.path("ExampleFolder", "_targets_pfudatabase.R"))

# Run the PFUAggDatabase pipeline
targets::tar_make(script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"))
```
